The Astropy Project

### 2017-11-11 main.tex
Update on Overleaf.

\section*{Global TODO items}
\begin{itemize}
    \item subpackage not sub-package!
    \item spell check!
\end{itemize}

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
% heavily edited by Adrian PW - let me know if you want to revert anything!
All astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, from software packages that enable individualized
scientific research to data reduction tools and pipelines that enable
collaborations and survey operations.
Some such software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community, and the \astropypkg
core package a feature-rich library for \python-based astronomical software.

@@

For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).

@@

\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

Development has continued after the release of v2.0 of \package{astropy}.    The most significant development for the next release will be removing python 2 support \cite{ape10}.   While the v2.0 release is a ‘long term stable’ release )meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.  This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.   The v3.0 release is currently scheduled for December 2017.

In the release cycle after v3.0, the \astropy project will focus on optimization of the code and improved documentation for the v3.1 release.   To prepare for this release, software for testing and monitoring the performance of the code are being developed.   Less new functionality may be introduced in this release, but the focus will be primarily on improved performance.  In addition, a new suite of tutorials and documentation are being prepared for this release.

Beyond the core code, the \astropy project is also further developing the affiliated packages.  This includes elevating a suite of packages into part of the core project.    While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.   Some of these new efforts includes an initiative to develop tools for spectroscopy , integration of LSST software , and packages to support HEALPIX projection.

@@

\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

>>>>

\section*{Global TODO items}
\begin{itemize}
    \item subpackage not sub-package!
    \item spell check!
    \item check consistent astropy usage
\end{itemize}

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
% heavily edited by Adrian PW - let me know if you want to revert anything!
All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
for astronomical tasks: from scripts that enable individualized scientific research to software packages that enable collaborations to data reduction pipelines for survey operations.
Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community, and the \astropypkg
core package a feature-rich library for \python-based astronomical software.

@@

For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).

@@

\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   An example of this is given in \figurename \ref{fig:convolution-example}.  In version $<=1.3$, the direct convolution and fast fourier transform (fft) convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

Development has continued after the release of v2.0 of \package{astropy}.    The most significant development for the next release will be removing python 2 support \citep{ape10}.  While the v2.0 release is a ‘long term stable’ release (meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.  This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.   The v3.0 release is currently scheduled for December 2017.

In the release cycle after v3.0, the \astropy project will focus on optimization of the code and improved documentation for the v3.1 release. To prepare for this release, software for testing and monitoring the performance of the code are being developed.   Less functionality may be introduced in this release while the focus will be primarily on improved performance.  In addition, a new suite of tutorials and documentation are being prepared for this release.

Beyond the core code, the \astropy project is also further developing the affiliated packages.  This includes elevating a suite of packages into part of the core project. While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.   Some of these new efforts includes an initiative to develop tools for spectroscopy, integration of LSST software, and packages to support HEALPIX projection.

@@

\inlinecomment{SMC: Can a brief description of each code be added?}
\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}
